%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Software Engineer}
  {Bloomberg}
  {London, UK}
  {Aug 2018 - Present}
  {
  \begin{cvitems}
    \item {Working on MARS (Multi Asset Risk System) using Python/C++/JavaScript.}
    \item {I am also the tech rep for the team and responsible for learning about new technologies
      and using them to build new tools and enhance systems which have an impact on multiple different
      teams at Bloomberg.}
  \end{cvitems}
  }

\cventry
  {Technology Summer Analyst}
  {Citigroup}
  {London, UK}
  {Jun 2017 - Aug 2017}
  {
  \begin{cvitems}
    \item {Set up Grafana and Logstash to build a capacity monitoring application
      using Elasticsearch.}
    \item {Used Python and Elasticsearch API to set up a unique data pipeline
      with Graphite as the data source which enabled us to create more powerful
      and detailed data visualisations.}
    \item {Researched into alternative tools like StatsD and Carbon Aggregator
      in order to set up the unique data pipeline.}
    \item {Configured and deployed Logstash, Elasticsearch and Grafana on CentOS to create
      a dashboard to monitor important server metrics.}
  \end{cvitems}
  }


\cventry
  {Software Engineer}
  {UCL Information Services Division}
  {London, UK}
  {Mar 2017 - Jun 2018}
  {
  \begin{cvitems}
    \item {Using Python to create API's around UCL's digital services for establishing an ecosystem of third party UCL apps.}
    \item {Used React and Django to create a website to manage room bookings in UCL.}
    \item {Built a documentation template for API's using React and Material-UI.}
  \end{cvitems}
  }


\cventry
  {Software Engineering Intern}
  {Activate Technologies}
  {London, UK}
  {Jun 2016 - Sept 2016}
  {
    \begin{cvitems}
      \item {Created a platform to build and run multiple Facebook Messenger
        bots from the same server, thus, cutting costs considerably.}
      \item {Used Express.js, Node.js, MongoDB and D3.js to build the backend
        for the platform, CMS and the analytics dashboard.}
    \end{cvitems}
  }

% \cventry
%   {Open Source Projects Coordinator}
%   {Engineers Without Borders UCL}
%   {London, UK}
%   {Oct 2015 - Present}
%   {
%     \begin{cvitems}
%       \item {Started a Github organisation for EWB UCL where students build open source software needed by NGO's.}
%       \item {Responsible for contacting NGO's for projects and organising meetups for students to plan and develop projects.}
%     \end{cvitems}
%   }

%---------------------------------------------------------
\end{cventries}
